Can Auxiliary Indicators Improve COVID-19 Forecasting and Hotspot Prediction?

### 2021-06-21 forecast/paper/paper.tex
Update acks, other small edits

The indicators we focus on provide information not generally available from
standard public health reporting. Among the many auxiliary indicators collected
in the API, we study the following five:  
\begin{itemize}
\item Change Healthcare COVID-like illness (CHNG-CLI): The percentage of
  outpatient visits that are primarily about COVID-related symptoms, based on
  de-identified Change Healthcare claims data.
\item Change Healthcare COVID (CHNG-COVID): The percentage of outpatient visits
  with confirmed COVID-19, based on the same claims data.
\item COVID Trends and Impact Survey COVID-like illness in the community
  (CTIS-CLI-in-community): The estimated percentage of the population who know
  someone in their local community that is sick, based on Delphi's COVID Trends
  and Impact Survey, in partnership with Facebook.
\item Doctor Visits COVID-like illness (DV-CLI): The same as CHNG-CLI, but
  computed based on de-identified medical insurance claims from other health
  systems partners.  
\item Google search trends for anosmia and ageusia (Google-AA): A measure of  
  Google search volume for queries that relate to anosmia or ageusia (loss of
  smell or taste), based on Google's COVID-19 Search Trends data set.  
\end{itemize}
In short, we choose these indicators because, conceptually speaking, they
measure aspects of an individual's disease progression that would plausibly
precede the occurence of (at worst, co-occur  with) the report of a positive
COVID-19 test, through standard public health reporting streams.

@@

\begin{figure}[tb!]
  \includegraphics[width=\columnwidth]{fig/revisions.pdf}
  % RJT: Ensuring we start with a "declarative title" :) 
  % https://www.internationalscienceediting.com/how-to-write-a-figure-caption/
  \caption{Revision behavior for two signals in the HRR containing New York  
    City.  Each colored line corresponds to the data as reported on a particular 
    date (\textit{as of} dates varying from September 28 through October
    19). The left panel shows the DV-CLI signal, which was regularly revised
    throughout the period, though the effects fade as we look further back in   
    time. In contrast, the right panel shows case rates reported by JHU CSSE
    (smoothed with a 7-day trailing average), which remain ``as reported'' on
    September 28, with a spike towards the end of this period, until a major
    correction is made on October 19, which brings this down and affects all
    prior data as well.}  
  \label{fig:vintage}
\end{figure}

@@

\acknow{We thank Matthew Biggerstaff, Logan Brooks, Johannes Bracher, Michael 
  Johansson, Evan Ray, Nicholas Reich, and Roni Rosenfeld for several
  enlightening conversations about forecast scoring and evaluation.  
  This material is based on work supported by gifts from Facebook, Google.org,
  the Foundation, and Optum; Centers for Disease Control and Prevention (CDC)
  grant U01IP001121; the Canadian Statistical Sciences Institute; National
  Sciences and Engineering Research Council of Canada (NSERC) grant
  RGPIN-2021-02618; and National Science Foundation Graduate Research Fellowship 
  Program (NSF GRFP) award DGE1745016.}

>>>>

The indicators we focus on provide information not generally available from
standard public health reporting. Among the many auxiliary indicators collected
in the API, we study the following five:  
\begin{itemize}
\item Change Healthcare COVID-like illness (CHNG-CLI): The percentage of
  outpatient visits that are primarily about COVID-related symptoms, based on
  de-identified Change Healthcare claims data.
\item Change Healthcare COVID (CHNG-COVID): The percentage of outpatient visits
  with confirmed COVID-19, based on the same claims data.
\item COVID Trends and Impact Survey COVID-like illness in the community
  (CTIS-CLI-in-community): The estimated percentage of the population who know
  someone in their local community thatwho is sick, based on Delphi's COVID Trends
  and Impact Survey, in partnership with Facebook.
\item Doctor Visits COVID-like illness (DV-CLI): The same as CHNG-CLI, but
  computed based on de-identified medical insurance claims from other health
  systems partners.  
\item Google search trends for anosmia and ageusia (Google-AA): A measure of  
  Google search volume for queries that relate to anosmia or ageusia (loss of
  smell or taste), based on Google's COVID-19 Search Trends data set.  
\end{itemize}
In short, we choose these indicators because, conceptually speaking, they
measure aspects of an individual's disease progression that would plausibly
precede the occurence of (at worst, co-occur  with) the report of a positive
COVID-19 test, through standard public health reporting streams.

@@

\begin{figure}[tb!]
  \includegraphics[width=\columnwidth]{fig/revisions.pdf}
  % RJT: Ensuring we start with a "declarative title" :) 
  % https://www.internationalscienceediting.com/how-to-write-a-figure-caption/
  \caption{Revision behavior for two indicators in the HRR containing Charlotte, 
    North Carolina.  Each colored line corresponds to the data as reported on a
    particular date (\textit{as of} dates varying from September 28 through
    October 19). The left panel shows the DV-CLI signal, which was regularly
    revised throughout the period, though the effects fade as we look further
    back in time. In contrast, the right panel shows case rates reported by JHU
    CSSE (smoothed with a 7-day trailing average), which remain ``as reported''
    on September 28, with a spike towards the end of this period, until a major 
    correction is made on October 19, which brings this down and affects all
    prior data as well.}  
  \label{fig:vintage}
\end{figure}

@@

\acknow{We thank Matthew Biggerstaff, Logan Brooks, Johannes Bracher, Michael 
  Johansson, Evan Ray, Nicholas Reich, and Roni Rosenfeld for several
  enlightening conversations about forecast scoring and evaluation.  
  This material is based on work supported by gifts from Facebook, Google.org,
  the McCune Foundation, and Optum; Centers for Disease Control and Prevention
  (CDC) grant U01IP001121; the Canadian Statistical Sciences Institute; National 
  Sciences and Engineering Research Council of Canada (NSERC) grant
  RGPIN-2021-02618; and National Science Foundation Graduate Research
  Fellowship Program (NSF GRFP) award DGE1745016.}
